Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-22 paper.tex
update

\todo[inline]{How does the following bisimulation relation
  compare to the one used in the Blame and Coercion paper?
  Are there any guiding principles to how this bisimulation
  relation was constructed? -JS}

@@

\todo[inline]{Give the motivation for the following lemma. Where
  does it get used? As in, which case of which other lemma or theorem? -JS}

@@

\todo[inline]{An extra property is required after changing case to small-step 
  -KC}

@@

We prove the equivalence among two \effCEK{C} machines with a strong
bisimulation. This time almost all the bisimulation relations are all
derived from definitions except the relaton for casts, which is by
cast constructors:
\todo[inline]{By ``derived from the definitions'' do you mean
 that it is a congruence? -JS}

@@

\todo[inline]{Standardize theorem statement -KC}
\begin{lemma}[Strong Bisimulation among $\mathcal{S}(\cdot)$]
	\label{thm:CEKS-bisim}
	If 
	$C_1$ and $C_2$ are instances of Lazy D Cast ADT,
	$s_1, s_1' \in S(C_1)$ and $s_2,s_2' \in S(C_2)$,
	$s_1 \approx s_2$,
	$\judgeSreduce{C_1}{s_1}{s_1'}$, and
	$\judgeSreduce{C_2}{s_2}{s_2'}$, then 
	$s_1' \approx s_2'$

	Or diagrammatically, 
	\[\begin{array}{clc}
	s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_1'\\
	\rotatebox[origin=c]{90}{$\approx$} 
	& & \rotatebox[origin=c]{90}{$\approx$} \\
	s_{2} & 
	\longrightarrow_{\text{\ineffCEKD}} & s_2' \\
	\end{array}\]
\end{lemma}
\begin{proof} 
  This proof is effectively a duplication of the transition rule of
  \effCEK{S(C)}.
%
  \todo[inline]{The above sentence is not normal proof jargon.  Are
    you doing a proof by cases on $s_{1}
    \longrightarrow_{\text{\effCEK{C}}} s_1'$? -JS}
%
  The key ideas of this proof are undoing sequencing with the property
  (2) of Lazy D Cast ADT, and handling all possibly uses of
  $cast(T,l,T)$ with property (3)-(11).
\end{proof}

\begin{proposition}[Equivalence of two \lazyD{} Cast ADTs]
  \label{thm:surely-lazyD-eqv}
  Suppose $C_1$ and $C_2$ are \lazyD\ Cast ADTs.
  If $\judgetype{\emptyset}{e}{T}$, $o : T$, then
  \[
  eval_{S(C_1)} = eval_{S(C_2)}.
  \]
\end{proposition}
\begin{proof}
  By induction with the help of Lemma~\ref{thm:CEKS-bisim}.
  \todo[inline]{Induction on what? -JS}
\end{proof}

>>>>

\todo[inline]{How does the following bisimulation relation
  compare to the one used in the Blame and Coercion paper?
  Are there any guiding principles to how this bisimulation
  relation was constructed? -JS
\\---\\
The guiding principle is to keep the change in D side atomic. \\
In the blame and coercion paper,
the bisimulation relation between $ \lambda{}C $ and $ \lambda{}S $ seems to be 
related, but its (iii) rules in Figure 6 looks wired to me. -KC}

@@

\todo[inline]{Give the motivation for the following lemma. Where
  does it get used? As in, which case of which other lemma or theorem? -JS
\\---\\
Partially fixed. Will say in which cases after finishing the bisim proof. -KC}

We use the following lemma in our bisimulation proof.

@@

@@

We prove the equivalence among two \effCEK{C} machines with a strong
bisimulation. The bisimulation relation is the smallest congruence relation 
that also includes the pairs induced by the rules below.
\todo[inline]{By ``derived from the definitions'' do you mean
 that it is a congruence? -JS
\\---\\
Exactly, fixed. -KC}

@@

\todo[inline]{Standardize theorem statement -KC}
\begin{lemma}[Strong Bisimulation among $\mathcal{S}(\cdot)$]
	\label{thm:CEKS-bisim}
	Assume $C_1$ and $C_2$ implements Lazy D Cast ADT
	$s_{1} \in \text{\effCEK{C_1}}$,
	$s_{2} \in \text{\effCEK{C_2}}$,
	$s_{1} \approx s_{2}$,
	\begin{enumerate}
		\item If $s_1 = \sOOhalt{o}$ then $s_2 = \sOOhalt{o}$
		\item If $s_2 = \sOOhalt{o}$ then $s_1 = \sOOhalt{o}$
		\item If $\judgeSreduce{C}{s_1}{s_3}$ 
		then $\judgeDreduce{s_2}{s_4}$ and $s_3 \approx s_4$ for some $s_4$
		\item If $\judgeSreduce{C}{s_2}{s_4}$ 
		then $\judgeDreduce{s_1}{s_3}$ and $s_3 \approx s_4$ for some $s_3$
	\end{enumerate}
%	If 
%	$C_1$ and $C_2$ are instances of Lazy D Cast ADT,
%	$s_1, s_1' \in S(C_1)$ and $s_2,s_2' \in S(C_2)$,
%	$s_1 \approx s_2$,
%	$\judgeSreduce{C_1}{s_1}{s_1'}$, and
%	$\judgeSreduce{C_2}{s_2}{s_2'}$, then 
%	$s_1' \approx s_2'$
%	
	Or diagrammatically, 
	\[\begin{array}{clc}
	s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_1'\\
	\rotatebox[origin=c]{90}{$\approx$} 
	& & \rotatebox[origin=c]{90}{$\approx$} \\
	s_{2} & 
	\longrightarrow_{\text{\ineffCEKD}} & s_2' \\
	\end{array}\]
\end{lemma}
\begin{proof} By casing on $s_{1} \approx s_{2}$.
%
  \todo[inline]{The above sentence is not normal proof jargon.  Are
    you doing a proof by cases on $s_{1}
    \longrightarrow_{\text{\effCEK{C}}} s_1'$? -JS
\\---\\
By casing on the bisimulation relation. -KC}
%
  The key ideas of this proof are undoing sequencing with the property
  (2) of Lazy D Cast ADT, and handling all possibly uses of
  $cast(T,l,T)$ with property (3)-(11).
\end{proof}

\begin{proposition}[Equivalence of two \lazyD{} Cast ADTs]
  \label{thm:surely-lazyD-eqv}
  Assume $C_1$ and $C_2$ implements Lazy D Cast ADT,
  \[
  eval_{\mathcal{S}(C_1)} = eval_{\mathcal{S}(C_2)}.
  \]
\end{proposition}
\begin{proof}
	Without lost of generality, assume $\judgeSreduce{C_1}{e}{o}$, prove 
	$\judgeSreduce{C_2}{e}{o}$.\\
	By the definition of $eval_{\mathcal{S}(C)}$, we know 
	\[
	\judgeSreduceTrans{C_2}{load_{\mathcal{S}(C_1)}(e)}{\sOOhalt{o}}
	\]
	By induction on this reduction sequence and Lemma~\ref{thm:CEKS-bisim}, we 
	have 
	\[\judgeSreduceTrans{C_2}{load_{\mathcal{S}(C_2)}(e)}{\sOOhalt{o}}\]
	that is, $\judgeSreduce{C_2}{e}{o}$
\todo[inline]{Induction on what? -JS
\\---\\
Fixed. -KC
\\---\\
Need to define load. -KC}
\end{proof}
